Maintenance planning on French military aircraft operations

### 2018-01-15 latex/ROADEF2018/article_roadef_2018_alt.tex
corrected ROADEF article and cleaned old ROADEF article files

\section{Introduction}
    The Military Flight and Maintenance Planning Problem considered here aims to assign missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modeled geographically since a round-trip to the base is assumed for each flight. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008,Verhoeff2015}, it has not received as much attention as the latter. In the following, the problem with already scheduled missions is considered.

@@

    Resources require recurrent preventive maintenance operations since the realization of tasks diminish the remaining usage time of resources. A resource cannot be used for a task $j$ if its remaining usage time is less that usage $h_j$ required by task $j$. A maintenance operation assigns to the resource exactly $H$ units of remaining usage time. The remaining usage time not used before the maintenance operation is lost. %Independently of its usage, each resource has to be maintained each $t^u$ periods of time since the end of the last maintenance operation. 
		A maintenance operation takes exactly $m$ periods and cannot be interrupted: during this time the resource cannot be assigned to any task. Some resources can be in maintenance at the beginning of the planning horizon, $n_t$ is used for the number of aircraft in such planned maintenance per period $t$ and defined only for the first $m-1$ time periods. In the next section, we present a new mathematical model for this problem.
    % We will call "remaining elapsed time" (or $ret$) to the amount of time that needs to pass in order for the resource to need a maintenance at any given period.

>>>>

\section{Introduction}
    The Military Flight and Maintenance Planning Problem considered here aims to assign missions and maintenance tasks to military aircraft. It is a variant of the Flight and Maintenance Planning problem where flights are not modeled geographically since a round-trip to the base is assumed for each flight. It also includes different objectives and constraints. Although the former has been studied in literature in \cite{Cho2011,Chastellux2017,Kozanidis2008,Verhoeff2015}, it has not received as much attention as the latter. In the following, the problem with already scheduled missions is considered. With respect to \cite{Chastellux2017}, a new model will be presented.

@@

    Resources require recurrent preventive maintenance operations since the realization of tasks diminish their remaining usage time. A resource cannot be used for a task $j$ if its remaining usage time is less than usage $h_j$ required by task $j$. A maintenance operation assigns to the resource exactly $H$ units of remaining usage time. The remaining usage time not used before the maintenance operation is lost. %Independently of its usage, each resource has to be maintained each $t^u$ periods of time since the end of the last maintenance operation. 
		A maintenance operation takes exactly $m$ periods and cannot be interrupted: during this time the resource cannot be assigned to any task. Some resources can be in maintenance at the beginning of the planning horizon, $n_t$ is used for the number of aircraft in such planned maintenance per period $t$ and defined only for the first $m-1$ time periods. In the next section, we present a new mathematical model for this problem.
    % We will call "remaining elapsed time" (or $ret$) to the amount of time that needs to pass in order for the resource to need a maintenance at any given period.
